\documentclass[journal]{new-aiaa}
%\documentclass[conf]{new-aiaa} for conference papers
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\usepackage[section]{placeins}


%\usepackage{cite}


\setlength\LTleft{0pt} 

\title{Perceptron Q-learning applied to Super Smash Bros Melee}

\author{Liam Brown \footnote{Graduate Student, Aeronautics and Astronautics.} and Jeremy Crowley\footnote{Graduate Student, Aeronautics and Astronautics.}}
\affil{Stanford University, Stanford, CA, 94305}

\begin{document}

\maketitle

\begin{abstract}
Reinforcement learning (RL) has been shown to produce optimal policies in environments with small discrete state and action spaces, but has significant limitations when the state-action space is continuous. Discretization techniques can solve the issue of continuous state-action spaces, however this often results in intractable runtimes for the learning algorithm. In this paper, we discuss a reinforcement learning strategy for the video game Super Smash Bros Melee, a game that has a large state-action, by applying global approximation in the Q-learning algorithm. We train the algorithm on progressively harder opponents and show that the agent is able to obtain better metrics.
\end{abstract}


%
% Introduction
%
\input{Introduction.tex}


%
% Related Work
%
\input{Related.tex}


%
% Applications to Super Smash Bros Melee
%
\input{Applications.tex}


%
%Novel approaches to state evolution
%
\input{Novelty.tex}


%
% Results
%
\input{Results.tex}


%
% Conclusion
%
\input{Conclusion}


%
% Appendix
%
\section*{Appendix}

An Appendix, if needed, appears \textbf{before} research funding information and other acknowledgments.


%
% Funding Sources
%
\section*{Funding Sources}

We would like to thank mom and dad.


%
% Acknowledgments
%
\section*{Acknowledgments}

We would like to acknowledge libmelee for providing an open source solution to obtaining information about the game while it is being played.

% add bibliography
% DONT DO BILBIO STYLE

\bibliography{biblio}




\end{document}
